---
title: "Using a forceGraph"
author: "Greg Macfarlane"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## igraph
The `igraph` package is popular for studying networks of various kinds in R. 
The `igraph` library comes with its own plotting mechanism, but it is static and
difficult to control.

```{r igraphdemo}
library(igraph)
g <- graph.atlas(900)
plot(g)
```

## networkD3
Recently, the `networkD3` package has included a function to make pretty html
plots of graph-style objects. Unfortunately, the `networkd3` library is somewhat
picky in its formulation, so we have created a function that will plot the 
graph automatically.

```{r networkD3_demo}
library(networkD3)
data("MisLinks")
data("MisNodes")
forceNetwork(
  Links = MisLinks, Nodes = MisNodes, 
  Source = "source", Target = "target", Value = "value", 
  NodeID = "name", Group = "group", opacity = 0.9
)
```

## forceNetwork
The `simpleNetwork` function is better than the default `plot.igraph`, but 
is not flexible enough.

```{r simpleNetwork}

```

